How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-20 tse-paper/content.tex
Move figure
first round of edits on new introduction

Within the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
Build
logs are a textual by-product that automatic software build processes
create.
As a ``treasure trove'' of information, they contain results
not only of the elemntary steps to ``make'' a project---such as
retrieving and resolving dependencies, compiling, and testing the
software---but also about anciliary quality assurance steps such as
automated, static analysis tools.

When a build or one of its sub steps fails, developers typically
scavenge the log for the source of the error.
This manual activity is
tedious and prone to error~\cite{santolucito2018statically}.
As a
single build log can be over 50 megabytes large~\cite{beller2017oops},
it finding a piece of information in it is akin to searching for a
needle in a haystack.
In addition, due to their information richness,
build logs enable a plethora of other applications: with the help of
build logs, we can better understand and cateogrize Continuous
Integration failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive}, or
investigate static analysis tools in CI
builds~\cite{zampetti2017open}.
Manual analysis of build logs does not
scale to the number of build logs and amount of information that such
sophisticated applications require.
Therefore, being able to
automatically extract pieces of information from build logs
is not only paramount to such applications, but can also help
developers debug a broken build.

However, despite its paramount role, the process of how to analyze
build logs has so far received little attention, bringing us to our
first research question:
\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}

\begin{itemize}
  \item[\textbf{RQ1:}] What are the state-of-the-art techniques on build
  log analysis?
 \end{itemize}
\end{simplebox}

In this article, as first step (\Cref{fig:overview}), we show that
less than half of the 61 works which rely on build log analysis
describe how they performed it, and even fewer did so in detail, let
alone made their implementation available.
Even so, the literature
survey finds three main strategies to extract information chunks from
build logs: Using 1) a set of manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops}, 2) a list of keywords
to identify regions of interest in the build log, and 3)
% TODO (Caro): Provide better description
doing text-similarity.

@@

\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
\begin{itemize}
  \item[\textbf{RQ2:}] What are the comparative strengths and weaknesses
  of the top-3 build log anaylsis techniques?
\end{itemize}
\end{simplebox}

To answer this question, we implement three automatic techniques for
build log analysis based on the three stratgies at large (step 2):

@@

In step 3, we conduct an empirical study to gauge the performance of
these chunk retrieval techniques under a variety of conditions in
real-world projects.
Finally, we develop guidelines (step 4) on when
one of the techniques might be perferrential to its alternatives.

@@

% % \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
% to retrieve information from continuous integration build logs.
% % \textbf{RQ2} is refined into sub-questions along with the criteria
% resulting from \textbf{RQ1} and compares their instantiations for the
% three techniques:
% % how many training examples a technique needs to perform best
% (\textbf{RQ2.1}), how structurally diverse the examples can
% be (\textbf{RQ2.2}) and how accurate the retrieved output is
% (\textbf{RQ2.3}).
% % To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
% which encompasses about 800 log files from 80 repositories.
% % Each log is labeled with the log part describing the reason a build
% failed, keywords to search for this log part and a categorization of
% the labeled log part according to its structural representation within
% the log.

% Our study of the three techniques on \emph{LogChunks} shows that
% \begin{itemize}
%   \item PBE yields very accurate results when trained with two examples
%   from a
%   single structural category.
%   \item CTS shows the best average precision, though precision and
% recall
%   of a
%   retrieval is hard to determine from the given result.
%   A small increase in the number of training examples has no noticeable
%   influence.

%   Fewer structural categories improve precision and recall of the
%   retrieval.
%   \item KWS has the highest recall of all techniques, however much
%   lower precision.
%   It is the technique with the best recall when multiple structural
%   categories
%   are present in the training examples.
% \end{itemize}

% % \noindent
% % \textbf{Our work contributes:}
% % \begin{itemize}
% %   \item A tool with three prototypical implementations of chunk
% retrieval techniques:
% %	  \begin{itemize}
% %	    \item program synthesis from examples using the Microsoft
% PROSE library (PBE),
% %	    \item a common information retrieval approach using text
% similarity (CTS), and
% %	    \item a keyword search approach (KWS).
% %	  \end{itemize}
% %   \item Recommendations for the configuration of each of the
% investigated chunk retrieval techniques.
% %   \item Guidelines on choosing a suitable chunk retrieval technique.
% % \end{itemize}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
	\caption{Literature selection process, following
	\cite{petersen2015guidelines}.}
	\label{fig:lit-survey}
\end{figure}

@@

\lstset{
  morekeywords={INFO, WARN, 2008, 11, 09},
  alsoletter=-20819,
  keywordstyle=\bfseries\color{Plum},
  escapeinside=**
}
\begin{figure*}[htbp]
  \centering
  \lstinputlisting[breaklines=true]{listings/syslog.txt}
  \caption{System Log excerpt.
Example adapted from~\cite{he2017towards}.}
  \label{lst:system-log}
\end{figure*}

@@

We wanted to characterize how researchers use build logs as input to
any processes.
We were interested in
\begin{itemize}
  \item what information they are retrieving from the logs and
  what they use the retrieved information for (\textbf{RQ1.1})
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their
  tools (\textbf{RQ1.2})
  \item what kind of build logs they are using and the origin of these
  logs.
(\textbf{RQ1.3})
\end{itemize}
To objectifiy our data extraction we created a template of the targeted
factors and performed a pilot, as recommended by Petersen et
al.~\cite{petersen2015guidelines}.
Two authors extracted the data from five articles and we held a
consensus meeting to unify our understanding
of the data extraction template.
The remaining articles were divided over these two authors.
We inspected the articles as closely as necessary,
starting from occurrences of ``log'' or ``build'' within the text.

@@

\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-research on build
log analysis?}
\begin{itemize}
  \item[\textbf{RQ1.1:}] Which information is targeted?
  \item[\textbf{RQ1.2:}] Which techniques are used?
  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
\end{itemize}
\end{simplebox}

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language Processing}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}
% TODO one source might contribute multiple times to 'other'

@@

25\% of the articles claimed their implementation is available,
however we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating},
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
In addition we present our comparison baseline of random line
retrieval (RLR), illustrate the techniques on a concrete example
of log chunks and sketch out implementation.

@@

\begin{table*}[htbp]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}llXll@{}}
\toprule
Name			     & Acronym & Identification Technique
& Granularity & Configuration \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table*}

@@

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
a substring of the log file text, representing the
substring that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
If PROSE cannot synthesize a program, e.g.\
because the regular expression
necessary would be too complicated to synthesize, PBE returns the
error message ``no program found''.
\Cref{lst:prose-program-simplified} presents a simplified version
of a program learned from the examples in \Cref{lst:chunk-example}.
% TODO Caro: check that these figures are latest inserted here

@@

\subsection{Chunk Retrieval Example}
\label{seC:crt-example}

\begin{figure*}[!htbp]
  \centering
\begin{subfigure}[!htbp]{\columnwidth}
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[!htbp]{\columnwidth}
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
\end{subfigure}
  \caption{Two examples of log chunks explaining why an Android
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  % long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example}
\end{figure*}

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[!htbp]
  \centering
  \lstinputlisting[breaklines=true]{listings/prose.txt}
  \caption{Simplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example}}
  \label{lst:prose-program-simplified}
\end{figure}

\lstset{
  language=,
  morekeywords={},
  texcl=false
}
\begin{figure}[!htbp]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
=== RUN   TestSeparator
  \end{lstlisting}
  \vspace{-\baselineskip}
  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
=== RUN   TestGenerateHTML
  \end{lstlisting}
  \caption{Example of a log chunk showing a linter error}
  \label{lst:chunk-example-3}
\end{figure}

@@

\begin{simplebox}[minipage boxed title*=-2.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
retrieve chunks from build logs?}
\begin{itemize}
  \item[\textbf{RQ2.1:}] How many examples does a technique need to
  perform best?
  \item[\textbf{RQ2.2:}] How structurally similar do the examples
  need for a technique to be applicable?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

@@

	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}$ \vspace{0.05cm}\\
	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}

This concludes one execution within our evaluation.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the chunk retrieval
techniques PBE, CTS, KWS and RLR.

@@

When the training examples are of the same structure, one or two
two examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In our study, additional training
examples did not improve the chunk retrieval.
% In fact, unless they
% were in some sense redudant, adding training examples above that even
% hindered the applicability of PBE.

@@

\begin{simplebox}[minipage boxed title*=-7cm]{Caveat!}
This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrazies of our specific implementation of the
chunk retrieval techniques as well as the \emph{LogChunks}
data set.
\end{simplebox}

@@

\textbf{Implementation}
% TODO we need to say something about why we think that these
% limtiations do not actually harm our results
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
Our implementation of
PBE is based on the program synthesis provided by PROSE\@.
The
idiosyncrazies of this framework influence our PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

@@

\textbf{Refinement of Retrieval Quality for each Technique} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better approach the domain of build
logs.
The \emph{LogChunks} data set and our study results act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}[leftmargin=0.4cm] \itemsep1em
  \item \textbf{Custom Ranking and Tokens for PBE} The program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the FlashExtract DSL to fit common build log
  chunk retrieval tasks.
  FlashExtract includes special tokens when
  enumerating possible regular expressions.
  One could extend these
  with tokens found in build logs, such as ``-'',``='',``ERROR''
  or ``[OK''.
  \item \textbf{Meta-Parameter Optimization for CTS} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms and in stop words
  lists.
\end{itemize}

>>>>

Within the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
Build
logs are a textual by-product that automatic software build processes
create.
As a ``treasure trove'' of information, they contain results
not only of the elementary steps to ``make'' a project---such as
retrieving and resolving dependencies, compiling, and testing the
software---but also about ancillary quality assurance steps such as
automated static analysis tools.

When a build or one of its steps fails, developers typically
scavenge the log for the source of the error.
This manual activity is
tedious and prone to error~\cite{santolucito2018statically}.
As a
single build log can be over 50 megabytes large~\cite{beller2017oops},
finding a piece of information in it is akin to searching for a
needle in a haystack.
In addition, due to their information richness,
build logs enable a plethora of other applications: with the help of
build logs, we can better understand and categorize CI
failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive}, or
investigate static analysis tools in CI
builds~\cite{zampetti2017open}.
Manual analysis of build logs does not
scale to the number of build logs and amount of information that such
sophisticated applications require.
Therefore, being able to
automatically extract pieces of information from build logs
is not only paramount to applications such as the above mentioned
ones, but can also help
developers debug a broken build.

Despite its paramount role, the process of analyzing
build logs has so far received little attention, bringing us to our
first research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What are the state-of-the-research techniques on build log analysis?
\end{simplebox}

In this article, as first step (\Cref{fig:overview}), we show that
less than half of the 61 works which rely on build log analysis
describe how they performed it.
Even fewer did so in detail or
made their implementation available.
Through the literature
survey we identify three prevalent strategies to
analyze build logs: Using 1) a set of
manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops},
2) information
retrieval techniques,
and 3) a list of search keywords
to identify regions of interest in the build log.

@@

\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
2}}
What are the comparative strengths and weaknesses
of promising build log analysis techniques?
\end{simplebox}

To answer this question, we implement three automatic techniques for
build log analysis based on the identified strategies (step 2):

@@

In step 3, we conduct an empirical study to gauge the performance of
these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks} which encompasses build logs from
80 popular open source projects and a broad range of
build environments.
Finally, we develop guidelines (step 4) on when
one of the techniques might be preferential to its alternatives.

@@

To enable retracing of our research, we provide a detailed replication
package~\cite{brandt2020chunk-replication}.

@@

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
	\caption{Literature selection process, following
	\cite{petersen2015guidelines}.}
	\label{fig:lit-survey}
\end{figure}

\lstset{
  morekeywords={INFO, WARN, 2008, 11, 09},
  alsoletter=-20819,
  keywordstyle=\bfseries\color{Plum},
  escapeinside=**
}
\begin{figure}[b]
  \centering
  \lstinputlisting[breaklines=true]{listings/syslog.txt}
  \caption{System Log excerpt.
Example adapted from~\cite{he2017towards}.}
  \label{lst:system-log}
\end{figure}

@@

We wanted to characterize how researchers use build logs as input to
any processes.
We were interested in
\begin{itemize}
  \item what information they are retrieving from the logs and
  what they use the retrieved information for (\textbf{RQ1.1})
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their
  tools (\textbf{RQ1.2})
  \item what kind of build logs they are using and the origin of these
  logs.
(\textbf{RQ1.3})
\end{itemize}
To objectify our data extraction we created a template of the targeted
factors and performed a pilot, as recommended by Petersen et
al.~\cite{petersen2015guidelines}.
Two authors extracted the data from five articles and we held a
consensus meeting to unify our understanding
of the data extraction template.
The remaining articles were divided over these two authors.
We inspected the articles as closely as necessary,
starting from occurrences of ``log'' or ``build'' within the text.

@@

\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What are the state-of-the-research
techniques on build log analysis?}
\begin{itemize}[leftmargin=2cm]
  \item[\textbf{RQ1.1:}] Which information is targeted?
  \item[\textbf{RQ1.2:}] Which techniques are used?
  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
\end{itemize}
\end{simplebox}

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language Processing}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}

@@

25\% of the articles claimed their implementation is available,
however, we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating},
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}

\begin{table*}[htb]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}llXll@{}}
\toprule
Name			     & Acronym & Identification Technique
& Granularity & Configuration \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table*}

This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
In addition we present our comparison baseline of random line
retrieval (RLR), illustrate the techniques on a concrete example
of log chunks and sketch out implementation.

@@

@@

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
a substring of the log file text, representing the
substring that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
If PROSE cannot synthesize a program, e.g.\
because the regular expression
necessary would be too complicated to synthesize, PBE returns the
error message ``no program found''.
\Cref{lst:prose-program-simplified} presents a simplified version
of a program learned from the examples in \Cref{lst:chunk-example}.

@@

\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

\begin{figure}[tbp]
  \centering
\begin{subfigure}[tbp]{\columnwidth}
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[tbp]{\columnwidth}
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
\end{subfigure}
  \caption{Two examples of log chunks explaining why an Android
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  % long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example}
\end{figure}

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[tbp]
  \centering
  \lstinputlisting[breaklines=true]{listings/prose.txt}
  \caption{Simplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example}}
  \label{lst:prose-program-simplified}
\end{figure}

\lstset{
  language=,
  morekeywords={},
  texcl=false
}
\begin{figure}[tbp]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
=== RUN   TestSeparator
  \end{lstlisting}
  \vspace{-\baselineskip}
  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
=== RUN   TestGenerateHTML
  \end{lstlisting}
  \caption{Example of a log chunk showing a linter error}
  \label{lst:chunk-example-3}
\end{figure}

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} What are the comparative strengths and weaknesses
of promising build log analysis techniques?}
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] How many examples does a technique need to
  perform best?
  \item[\textbf{RQ2.2:}] How structurally similar do the examples
  need for a technique to be applicable?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

@@

	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}$

	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}
This concludes one execution within our evaluation.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the chunk retrieval
techniques PBE, CTS, KWS and RLR.

@@

When the training examples are of the same structure, one or two
two examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In our study, additional training
examples did not improve the chunk retrieval.
% In fact, unless they
% were in some sense redundant, adding training examples above that even
% hindered the applicability of PBE.

@@

\begin{simplebox}[minipage boxed title*=-7cm]{Caveat!}
This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrasies of our specific implementation of the
chunk retrieval techniques as well as the \emph{LogChunks}
data set.
\end{simplebox}

@@

\textbf{Implementation}
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
Our implementation of
PBE is based on the program synthesis provided by PROSE\@.
The
idiosyncrasies of this framework influence our PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

@@

\textbf{Refinement of Retrieval Quality for each Technique} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better approach the domain of build
logs.
The \emph{LogChunks} data set and our study results act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}[leftmargin=0.4cm]
  \item \textbf{Custom Ranking and Tokens for PBE} The program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the FlashExtract DSL to fit common build log
  chunk retrieval tasks.
  FlashExtract includes special tokens when
  enumerating possible regular expressions.
  One could extend these
  with tokens found in build logs, such as ``-'',``='',``ERROR''
  or ``[OK''.
  \item \textbf{Meta-Parameter Optimization for CTS} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms and in stop words
  lists.
\end{itemize}
